Parallel Nonnegative CP Decomposition \\ of Dense Tensors

### 2018-12-07 latex/slides/SIAM-ALA18/fig/plots.tex
added SIAM-ALA talk

% macros for plotting
\newcommand{\datafile}{}
\newcommand{\alg}{}
\newcommand{\numiterations}{30}
\newcommand{\minvalue}{1}

% toggles whether or not to plot naive results (if not, the rows of the data file also need to be commented out)
\newif\ifnaive
% toggles ksweep vs scaling plot
\newif\ifksweep
% toggles legend
\newif\iflegend
% toggles y axis label
\newif\ifylabel
% toggles wider plot area
\newif\ifwider
% toggles including liavas results
\newif\ifliavas
% toggles weak 3D 
\newif\ifweakthreeD

\newcommand{\setcolors}{
\pgfplotsset{cycle list={
	red, fill=red \\ 
	blue, fill=blue \\ 
	teal, fill=teal \\ 
	red, pattern=crosshatch, pattern color=red \\
	teal, pattern=crosshatch, pattern color=teal \\
	blue, pattern=crosshatch, pattern color=blue \\
}};
}

% set options for grouped bar plot
\newcommand{\breakdownplotoptions}{
	ybar stacked,
	reverse legend,
	bar width=8pt,
	%width=9cm, height=3.85cm,
	%width=\textwidth,
	ylabel={Time (s)}, 
	y label style={yshift=-.5cm},
	ymin=0,
	\ifweakthreeD
		symbolic x coords={D1,N1,D8,N8,D27,N27,D64,N64},
	\else
		symbolic x coords={D1,N1,D16,N16,D81,N81,D256,N256},
	\fi	
	xtick=data,
	legend style={at={(0.5,1.3)},anchor=north},
	legend columns=-1,
	reverse legend
}

>>>>

% macros for plotting
\newcommand{\alg}{}
\newcommand{\numiterations}{30}
\newcommand{\minvalue}{1}

% toggles whether or not to plot naive results (if not, the rows of the data file also need to be commented out)
\newif\ifnaive
% toggles ksweep vs scaling plot
\newif\ifksweep
% toggles legend
\newif\iflegend
% toggles y axis label
\newif\ifylabel
% toggles wider plot area
\newif\ifwider
% toggles including liavas results
\newif\ifliavas

\newcommand{\setcolors}{
\pgfplotsset{cycle list={
	red, fill=red \\ 
	blue, fill=blue \\ 
	green, fill=green \\ 
	red, pattern=crosshatch, pattern color=red \\
	green, pattern=crosshatch, pattern color=green \\
	blue, pattern=crosshatch, pattern color=blue \\
}};
}

% set options for grouped bar plot
\newcommand{\breakdownplotoptions}{
	ybar stacked,
	reverse legend,
	bar width=8pt,
	%width=9cm, height=3.85cm,
	%width=\textwidth,
	ylabel={Time (s)}, 
	y label style={yshift=-.5cm},
	ymin=0,
	symbolic x coords={D1,N1,D16,N16,D81,N81,D256,N256},
	xtick=data,
	legend style={at={(0.5,1.3)},anchor=north},
	legend columns=-1,
	reverse legend
}

### 2018-12-07 latex/slides/Sandia-LDRD-pres/talk.tex
added SIAM-ALA talk

\input{../sc18/fig/Alg_header.tex}

@@

\begin{center}
\scalebox{1.5}{
\only<1>{\input{../sc18/fig/AlgStart.tex}}
\only<2>{\input{../sc18/fig/AlgMTTKRP.tex}}
\only<3>{\input{../sc18/fig/AlgRS.tex}}
\only<4>{\input{../sc18/fig/AlgNLS.tex}}
\only<5>{\input{../sc18/fig/AlgAG.tex}}
}

@@

\begin{figure}
\centering
  \subfloat[Start]{\input{../sc18/fig/AlgStart.tex}} \quad
  \subfloat[Local MTTKRP]{\input{../sc18/fig/AlgMTTKRP.tex}} \quad
  \subfloat[Reduce-Scatter]{\input{../sc18/fig/AlgRS.tex}} \quad
  \subfloat[Local NLS]{\input{../sc18/fig/AlgNLS.tex}} \quad
  \subfloat[All-Gather]{\input{../sc18/fig/AlgAG.tex}}
\end{figure}
\end{frame}

@@

\input{../sc18/fig/dim_tree.tex}
\end{center}

@@

\input{../sc18/plots}

@@

\begin{figure}
\begin{tikzpicture}[scale=.9]
\renewcommand{\datafile}{../sc18/data/str_3D_syn.dat}
\renewcommand{\numiterations}{42}
\liavastrue
\strongscalingplot
\end{tikzpicture}
\caption{Strong scaling of 3D synthetic tensor with dimension $1024\times 1024\times 1024$ on processor grids $2^k\times 2^k\times 2^k$ for $k\in\{0,1,2,3\}$.  The rank is fixed at 32.}
\end{figure}

@@

\begin{figure}
\begin{tikzpicture}[scale=.9]
\renewcommand{\datafile}{../sc18/data/str_5D_syn.dat}
\renewcommand{\numiterations}{10}
\liavasfalse
\strongscalingplot
\end{tikzpicture}
\caption{Strong scaling of 5D synthetic tensor with dimension $64\times 64\times 64\times 64\times 64$ on processor grids $1\times1\times1\times1\times1$, $2\times1\times1\times1\times1$, $\dots$, $2\times2\times2\times2\times2$.  The rank is fixed at 32.}
\end{figure}

@@

\begin{figure}
\begin{tikzpicture}
\renewcommand{\datafile}{../sc18/data/wk_4D_syn.dat}
\renewcommand{\numiterations}{10}
\breakdownplot
%\labels
\end{tikzpicture}
\caption{Weak scaling of 4D synthetic tensors with (D) and without (N) the use of dimension trees.  The tensor and processor grid dimensions are $128k\times 128k\times 128k\times 128k$ and $k\times k\times k\times k$ for $k\in\{1,2,3,4\}$, and the rank is fixed at 32.}
\end{figure}

@@

\begin{figure}
\renewcommand{\datafile}{../sc18/data/ksw_4D_HSI.dat}
\renewcommand{\numiterations}{10}
\begin{tikzpicture}[scale=.8]
\begin{axis}[	
	ybar stacked,
	bar width=12pt,
	width=\columnwidth,
	height =.5\columnwidth,
	%width=9cm, height=3.85cm,
	ylabel={Time (s)}, 
	xlabel={Rank $k$},
	y label style={yshift=-.5cm},
	ymin=0,
	%symbolic x coords={D10,N10,,D20,N20,,D30,N30,,D40,N40,,D50,N50},
	symbolic x coords={D10,D20,D30,D40,D50},
	%xtick=data,
	xticklabels={,10,,20,,30,,40,,50},
	legend style={at={(0.5,1.3)},anchor=north},
	legend columns=-1,
]
	\setcolors
	\addplot table[x=alg-K, y expr=(\thisrow{mttkrp}/(\minvalue*\numiterations))] {\datafile};
	\addplot table[x=alg-K, y expr=(\thisrow{mttv}/(\minvalue*\numiterations))] {\datafile};
	\addplot table[x=alg-K, y expr=((\thisrow{nnls}+\thisrow{gram})/(\minvalue*\numiterations))] {\datafile};
	\addplot table[x=alg-K, y expr=((\thisrow{allgather}+\thisrow{reducescatter})/(\minvalue*\numiterations))] {\datafile};
	\addplot table[x=alg-K, y expr=(\thisrow{allreduce}/(\minvalue*\numiterations))] {\datafile};
	\legend{PM,mTTV,NLS,Factor Comm,Gram Comm};
\end{axis}
%\labels
\end{tikzpicture}
\caption{Per-iteration time breakdown of our implementation (using dimension trees) over various ranks for a time-lapse HSI dataset with dimensions $1344\times 1024\times 33 \times 9$ on 64 processors arranged in a $8\times8\times1\times1$ grid.}
\end{figure}

>>>>

\input{../../sc18/fig/Alg_header.tex}

@@

\begin{center}
\scalebox{1.5}{
\only<1>{\input{../../sc18/fig/AlgStart.tex}}
\only<2>{\input{../../sc18/fig/AlgMTTKRP.tex}}
\only<3>{\input{../../sc18/fig/AlgRS.tex}}
\only<4>{\input{../../sc18/fig/AlgNLS.tex}}
\only<5>{\input{../../sc18/fig/AlgAG.tex}}
}

@@

\begin{figure}
\centering
  \subfloat[Start]{\input{../../sc18/fig/AlgStart.tex}} \quad
  \subfloat[Local MTTKRP]{\input{../../sc18/fig/AlgMTTKRP.tex}} \quad
  \subfloat[Reduce-Scatter]{\input{../../sc18/fig/AlgRS.tex}} \quad
  \subfloat[Local NLS]{\input{../../sc18/fig/AlgNLS.tex}} \quad
  \subfloat[All-Gather]{\input{../../sc18/fig/AlgAG.tex}}
\end{figure}
\end{frame}

@@

\input{../../sc18/fig/dim_tree.tex}
\end{center}

@@

\input{../../sc18/plots}

@@

\begin{figure}
\begin{tikzpicture}[scale=.9]
\renewcommand{\datafile}{../../sc18/data/str_3D_syn.dat}
\renewcommand{\numiterations}{42}
\liavastrue
\strongscalingplot
\end{tikzpicture}
\caption{Strong scaling of 3D synthetic tensor with dimension $1024\times 1024\times 1024$ on processor grids $2^k\times 2^k\times 2^k$ for $k\in\{0,1,2,3\}$.  The rank is fixed at 32.}
\end{figure}

@@

\begin{figure}
\begin{tikzpicture}[scale=.9]
\renewcommand{\datafile}{../../sc18/data/str_5D_syn.dat}
\renewcommand{\numiterations}{10}
\liavasfalse
\strongscalingplot
\end{tikzpicture}
\caption{Strong scaling of 5D synthetic tensor with dimension $64\times 64\times 64\times 64\times 64$ on processor grids $1\times1\times1\times1\times1$, $2\times1\times1\times1\times1$, $\dots$, $2\times2\times2\times2\times2$.  The rank is fixed at 32.}
\end{figure}

@@

\begin{figure}
\begin{tikzpicture}
\renewcommand{\datafile}{../../sc18/data/wk_4D_syn.dat}
\renewcommand{\numiterations}{10}
\breakdownplot
%\labels
\end{tikzpicture}
\caption{Weak scaling of 4D synthetic tensors with (D) and without (N) the use of dimension trees.  The tensor and processor grid dimensions are $128k\times 128k\times 128k\times 128k$ and $k\times k\times k\times k$ for $k\in\{1,2,3,4\}$, and the rank is fixed at 32.}
\end{figure}

@@

\begin{figure}
\renewcommand{\datafile}{../../sc18/data/ksw_4D_HSI.dat}
\renewcommand{\numiterations}{10}
\begin{tikzpicture}[scale=.8]
\begin{axis}[	
	ybar stacked,
	bar width=12pt,
	width=\columnwidth,
	height =.5\columnwidth,
	%width=9cm, height=3.85cm,
	ylabel={Time (s)}, 
	xlabel={Rank $k$},
	y label style={yshift=-.5cm},
	ymin=0,
	%symbolic x coords={D10,N10,,D20,N20,,D30,N30,,D40,N40,,D50,N50},
	symbolic x coords={D10,D20,D30,D40,D50},
	%xtick=data,
	xticklabels={,10,,20,,30,,40,,50},
	legend style={at={(0.5,1.3)},anchor=north},
	legend columns=-1,
]
	\setcolors
	\addplot table[x=alg-K, y expr=(\thisrow{mttkrp}/(\minvalue*\numiterations))] {\datafile};
	\addplot table[x=alg-K, y expr=(\thisrow{mttv}/(\minvalue*\numiterations))] {\datafile};
	\addplot table[x=alg-K, y expr=((\thisrow{nnls}+\thisrow{gram})/(\minvalue*\numiterations))] {\datafile};
	\addplot table[x=alg-K, y expr=((\thisrow{allgather}+\thisrow{reducescatter})/(\minvalue*\numiterations))] {\datafile};
	\addplot table[x=alg-K, y expr=(\thisrow{allreduce}/(\minvalue*\numiterations))] {\datafile};
	\legend{PM,mTTV,NLS,Factor Comm,Gram Comm};
\end{axis}
%\labels
\end{tikzpicture}
\caption{Per-iteration time breakdown of our implementation (using dimension trees) over various ranks for a time-lapse HSI dataset with dimensions $1344\times 1024\times 33 \times 9$ on 64 processors arranged in a $8\times8\times1\times1$ grid.}
\end{figure}
